### 2014-06-27 alex/albania.Rmd

```{r gender, echo=FALSE}

@@

>>>>

```{r gender, echo=FALSE}
df = student2012.sub %>% group_by(CNT, ST04Q01, OECD) %>% summarise(mmath = mean(math), mread = mean(read), msci = mean(sci))

@@

```{r OUTHOURS, echo=FALSE, fig.width=15}
#qplot(x = OUTHOURS, data = student2012.sub, facets = ~OECD, group = CNT) 
#ggplot(subset(student2012.sub, OECD == "Albania"), aes(x = OUTHOURS)) + geom_density(fill = "gray", alpha = I(0.7))
#ggplot(subset(student2012.sub, OECD == "OECD"), aes(x = OUTHOURS, fill = CNT)) + 
#  geom_density(alpha = I(0.1)) + scale_fill_manual(values = rep("gray", 34))
ggplot(subset(student2012.sub, !is.na(OUTHOURS)), aes(x = OUTHOURS, fill = CNT)) + geom_density(alpha = I(0.4)) + facet_wrap(~OECD)
```
